Figures for 3-D printed oxygen devices

### 2015-03-09 publishing/latex/plos_template.tex
working on discussion

\subsection*{Oxygen Control}
The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Figure \ref{figure1}.
Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
A different gas condition can be used in each sepereate iteration of the 6-well unit allowing 6 tecnical replicants of up to 4 different gas conditions in one 24 well plate\ref{figure2}.

\subsection*{Bioverifcation}
Bioverification of the devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.

@@

This device provides convenient oxygen control within a standard culture format.
This device adds oxygen control will still allowing standard assays and imaging to occur, with the addition of a source of the gas of interest.
3D-printing allows this design to be shared directly and modified by and end user without learning any microfabrication techniques.

The device is also reusable. Typical PDMS microfluidic chips for the control of oxygen conditions are single use due to biological material fouling the membrane gas permeability. 
Due the the non-permanent application, the membranes can be easily pealed off and replaced with fresh ones allowing the device to be reused.

Moving forward with additive manufacturing of microfluidic devices is desirable. 
3D printing higher levels of intricacy can be achieved without further complicating fabrication.
This allows any number of additional features to be added.
An on device mixer that could supply different levels of mixing between two sources of gas could reduce the number of tanks required.
A mixer could also allow more conditions in a single plate perhaps even 1 per well or even gradients within wells.
Even hight format plates such as 96 well plates could be used.
Gas connections could be reloated to allow stacking of device in incubators.

>>>>

\subsection*{Oxygen Control}
Oxygen control in the 24-well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Figure \ref{figure1}.
Oxygen was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
A different gas condition can be used in each sepereate iteration of the 6-well unit allowing 6 tecnical replicants of up to 4 different gas conditions in one 24 well plate\ref{figure2}.

\subsection*{Bioverifcation}
The devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.

@@

This new iteration of the multi-well insert for oxygen control maintains the convient features of the previous design.
Oxygen contol is preformed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often requried when cells are seeded within microfuildic chips.

This 3D-printed device improves on our previous design in a number of ways.
First, the fabrication is greatly simplified. 
No microfabrication, PDMS molding or Parylene coating is required.
3D-printing also enables higher levels of intricacy without any additional fabrication allowing us to include the distribution network and the pipe within a pipe design. 
Moving forward with additive manufacturing of microfluidic devices is desirable. 
A comprable PDMS device would require several additional microfabriated layers to be manually aligned to reporduce just the distribution newtork.
Additionally, the non-premanat addheasion of membranes to the 3D-part allow them to be removed and replaced if they are damaged.
In PDMS devices the layers are bonded permantly via plasma bonding so damage to a membrane is not repairable.

3D-printing allows this design to be shared directly and modified by an end user without requireing any microfabrication techniques.
An on device mixer that could supply different levels of mixing between two sources of gas could reduce the number of tanks required.
A mixer could also allow more conditions in a single plate perhaps even 1 per well or even gradients within wells.
Even hight format plates such as 96 well plates could be used.
Gas connections could be reloated to allow stacking of device in incubators.
